Burden and health-related quality of life among caregivers of people with motor neuron disease

### 2024-06-27 output/tables/tab_var_category.tex
Updates from Overleaf

Description of text & Score (100\%) \\ 
\hline
\textit{Caregiver-related factors} &  \\
\hline
\hspace{0.2cm} Age & Continuous \\ 
\hline
\hspace{0.2cm} Sex & Male; female \\ 
\hline
\hspace{0.2cm} Marital status & Married or partnership; never/formerly married \\ 
\hline
\hspace{0.2cm} Education level & Below university; university or above \\ 
\hline
\hspace{0.2cm} In paid employment & Yes; no \\ 
\hline
\hspace{0.2cm} Relationship with patient & Spouse/partner/child; other family/friend \\ 
\hline
\hspace{0.2cm} EQ-5D domains & Continuous (possible range 0-2) \\ 
\hline
\hspace{0.2cm} Duration spent caregiving & Continuous \\ 
\hline
\hspace{0.2cm} Average hours spent caring & Continuous \\ 
\hline
\textit{Patient-related factors} &  \\
\hline
\hspace{0.2cm} Age & Continuous \\ 
\hline
\hspace{0.2cm} Sex & Male; female \\ 
\hline
\hspace{0.2cm} Marital status & Married or partnership; never/formerly married \\ 
\hline
\hspace{0.2cm} Disease severity & Mild (37–48 ALSFRS pts); moderate/severe (\leq 36 pts)  \\ 
\hline
\hspace{0.2cm} Disease severity & Less severe (stage 1 or 2); more severe (stage 3 or 4)  \\ 
\hline
\hspace{0.2cm} Other (physical) condition & Yes; no \\ 
\hline
\hspace{0.2cm} Other (mental) condition & Yes; no \\ 
\hline
\hspace{0.2cm} MQOL psychological subscale & Continuous (possible range 0-10) \\ 
\hline
\hspace{0.2cm} MQOL existential subscale & Continuous (possible range 0-10) \\ 
\hline
\hspace{0.2cm} MHADS Anxiety & Continuous (possible range 0-18) \\ 
\hline
\hspace{0.2cm} MHADS Depression & Continuous (possible range 0-18) \\ 
\hline

>>>>

Description of text & Score (100\%) \\ 
\hline
\textit{Caregiver-related factors} &  \\
\hline
\hspace{0.2cm} Age & Continuous \\ 
\hline
\hspace{0.2cm} Sex & Male; Female \\ 
\hline
\hspace{0.2cm} Marital status & Married or partnership; Never/formerly married \\ 
\hline
\hspace{0.2cm} Education level & Below university; university or above \\ 
\hline
\hspace{0.2cm} In paid employment & Yes; no \\ 
\hline
\hspace{0.2cm} Relationship with patient & Spouse/partner/child; Other family/friend \\ 
\hline
\hspace{0.2cm} EQ-5D domains & Continuous (possible range 0-2) \\ 
\hline
\hspace{0.2cm} Duration spent caregiving & Continuous \\ 
\hline
\hspace{0.2cm} Average hours spent caring & Continuous \\ 
\hline
\textit{Patient-related factors} &  \\
\hline
\hspace{0.2cm} Age & Continuous \\ 
\hline
\hspace{0.2cm} Sex & Male; Female \\ 
\hline
\hspace{0.2cm} Marital status & Married or partnership; never/formerly married \\ 
\hline
\hspace{0.2cm} ALSFRS-Revised & Continuous (possible range 0-36)  \\ 
\hline
\hspace{0.2cm} King's stages (disease severity) & Less severe (stage 1/2); more severe (stage 3/4)  \\ 
\hline
\hspace{0.2cm} Any patient comorbidity & Yes; no \\ 
\hline
\hspace{0.2cm} Number of comorbidities & Continuous \\ 
\hline
\hspace{0.2cm} Rate of deterioration & Lowest; Medium; Highest \\ 
\hline
\hspace{0.2cm} MQOL psychological & Continuous (possible range 0-10) \\ 
\hline
\hspace{0.2cm} MQOL existential & Continuous (possible range 0-10) \\ 
\hline
\hspace{0.2cm} Modified-HADS Anxiety & Continuous (possible range 0-18) \\ 
\hline
\hspace{0.2cm} Modified-HADS Depression & Continuous (possible range 0-18) \\ 
\hline
